\texttt{bayesim}: a tool for fast model fitting with Bayesian inference

### 2018-09-04 paper/Manuscript.tex
updating figures

 \begin{figure}
   \includegraphics[width=0.9\columnwidth]{figure_1.png}
   \caption{\hl{(Figure copied from docs website for now, will make a publication-appropriate version)}}
   \label{fig1}
 \end{figure}

@@

  \begin{figure}
    \includegraphics[width=0.25\columnwidth]{structure.png}
    \includegraphics[width=0.65\columnwidth]{flowchart.png}
    \caption{Left: \texttt{bayesim} software structure. Right: Flowchart of use of \texttt{bayesim}.}
    \label{structure}
  \end{figure}

@@

  At this point, the inference loop can proceed. We start with a bounded prior distribution over the entire parameter space grid and the observed data in a randomized order. We feed in one piece of evidence (i.e. one observed data point) and compute the likelihood using a Gaussian. The standard deviation for each point in the parameter space is the sum of the experimental uncertainy of that observation and the model uncertainty at that point. The posterior distribution is computed as a Bayesian update on the prior. Next, we check whether the threshold condition for concentration of probability (defined as at least some percentage (by default 90\%) of the probability mass residing in at most some percentage (by default 5\%) of the parameter space volume. If this threshold is satisfied, the current posterior is stored and the prior reset to a uniform distribution. If not, the next observation is fed in. This procedure is repeated until the requisite number (by default, 80\%) of observed data points has been used, with the final posterior being the average of every stored posterior. The posterior is calculated in this way (rather than a Bayesian multiplication through every single observed point) to avoid numerical errors that can arise if very small numbers are multiplied together.

>>>>

 \begin{figure}
   \includegraphics[width=0.9\columnwidth]{figure_1.png}
   \caption{a) High-level flowchart of inputs and outputs to \texttt{bayesim}, b) 2D schematic of adaptive grid sampling approach.}
   \label{fig1}
 \end{figure}

@@

  \begin{figure}
    %\includegraphics[width=0.25\columnwidth]{structure.png}
    %\includegraphics[width=0.65\columnwidth]{flowchart.png}
    \includegraphics[width=0.95\columnwidth]{figure_2.png}
    \caption{a) \texttt{bayesim} software structure. b) Detailed flowchart of use of \texttt{bayesim}, with calculation steps and various levels of iteration indicated.}
    \label{structure}
  \end{figure}

@@

  At this point, the Bayesian inference loop can proceed. We start with a bounded prior distribution over the entire parameter space grid and the observed data in a randomized order. We feed in one piece of evidence (i.e. one observed data point) and compute the likelihood using a Gaussian. The standard deviation for each point in the parameter space is the sum of the experimental uncertainy of that observation and the model uncertainty at that point. The posterior distribution is computed as a Bayesian update on the prior. Next, we check whether the threshold condition for concentration of probability (defined as at least some percentage (by default 90\%) of the probability mass residing in at most some percentage (by default 5\%) of the parameter space volume. If this threshold is satisfied, the current posterior is stored and the prior reset to a uniform distribution. If not, the next observation is fed in. This procedure is repeated until the requisite number (by default, 80\%) of observed data points has been used, with the final posterior being the average of every stored posterior. The posterior is calculated in this way (rather than a Bayesian multiplication through every single observed point) to avoid numerical errors that can arise if very small numbers are multiplied together. This procedure of running the Bayesian loop multiple times until the desired number of pieces of evidence are used is encapsulated in the \texttt{Model.run()} function.
